Music Perception: Pilot Stimuli Analysis

### 2021-01-27 analysis/analysis.Rmd
update analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

## Stimuli
- Stimuli were selected from the previous study ([the sound of teaching music/experiment-1](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-1)).
- 48 stimuli were randomly chosen from each technique (either articulation or dynamics - therefore in total 96 stimuli). The half of them were selected from the teaching condition and the other half were from the performing condition.
  + 24 for teaching-articulation performances
  + 24 for performing-articulation performances
  + 24 for teaching-dynamics performances
  + 24 for performing-dynamics performances

@@

- 2 blocks (articulation / dynamics): participants were asked to do the same task for two expressions separately. The order of the blocks was counterbalanced across participants.
- 48 trials for each block (each stimulus was presented only once) and the stimuli were randomised across participants.

@@

Actual instruction:
```
Each performance was produced in order to either1) teach the musical expressive technique (as a teacher) 2) perform their best (as a performer).

@@

```{r packages, include = FALSE}
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
if (!require("afex")) {install.packages("afex"); require("afex")}
```

@@

t.test(ind_data_ad[Skill == "articulation"]$Percent, mu = 50, alternative = "two.sided")
```
- Not significantly different from chance (p > .2).

@@

# Accuracy for each stimulus
```{r export, echo = FALSE}
accuracy_data <- rbind(subset2, subset3)
accuracy_data <- accuracy_data[order(MidFile)]
accuracy_data

@@

# Judged as "teaching" for each stimulus
```{r teaching, echo = FALSE}
data$Teaching <- 0
data[rating == "Yes"]$Teaching <- 1

>>>>

## Stimuli
- Stimuli were selected from the previous study ([the sound of teaching music/experiment-1](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-1)).
- 48 stimuli were randomly chosen from each technique (either articulation or dynamics - therefore in total 96 stimuli). The half of them was selected from the teaching condition and the other half was from the performing condition.
  + 24 for teaching-articulation performances
  + 24 for performing-articulation performances
  + 24 for teaching-dynamics performances
  + 24 for performing-dynamics performances

@@

- 2 blocks (articulation / dynamics): participants were asked to do the same task for two techniques (expressions) separately. The order of the blocks was counterbalanced across participants.
- 48 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented across participants.

@@

Actual instruction:
```
Each performance was produced in order to either 1) teach the musical expressive technique (as a teacher) or 2) perform their best (as a performer).

@@

```{r packages, include = FALSE}
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
```

@@

t.test(ind_data_ad[Skill == "articulation"]$Percent, mu = 50, alternative = "two.sided")
```

@@

# Accuracy (%) for each stimulus
```{r export, echo = FALSE}
accuracy_data <- rbind(subset2, subset3)
accuracy_data <- accuracy_data[order(MidFile)]
accuracy_data

@@

# Judged as "teaching" (%) for each stimulus
```{r teaching, echo = FALSE}
data$Teaching <- 0
data[rating == "Yes"]$Teaching <- 1

### 2021-01-27 analysis/stimuli/stimuli_analysis.Rmd
update analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

## Results
- 1. [Accuracy](https://github.com/atsukotominaga/perception-v1.0/blob/master/analysis/analysis.Rmd)

@@

In order to see which stimulus was recognised as teaching performances, we decided to run exploratory analysis. We plotted correlations between each DV and the percentage of judgement as "teaching" regardless of their original conditions (i.e., teaching vs. performing).

>>>>

## Results
- 1. [Accuracy (private repo)](https://github.com/atsukotominaga/perception-v1.0/blob/master/analysis/analysis.Rmd)

@@

In order to see which stimulus was recognised as teaching performances, we decided to run exploratory analysis. We plotted relationships between each DV and the percentage of judgement as "teaching" for each stimulus regardless of their original conditions (i.e., whether each stimulus was coming from the teaching or performing condition).
